\documentclass{fonts}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{Pushpinder Pal Singh}{ 
\urlstyle{same}\href{https://swifti.ng}{swifti.ng} | \href{https://github.com/swiftlysingh}{github/swiftlysingh} | \href{mailto:pushpinderpal19@gmail.com}{pushpinderpal19@gmail.com}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\textbf{\href{https://www.gojek.io/}{\runsubsection{Software Engineer - Mobile |}}} 
\descript{GOJEK \datetext{May '22 – Aug '24}}
\begin{tightemize}
    \item Revamped Help Center UI using \emphitalic{UIKit}, improving usability and reducing support queries by \italictext{15\%}.
    \item Led crucial iOS initiatives for Help Center by collaborating seamlessly with Android, backend, and product teams.
    \item Built a Pin-based Auth SDK in \emphitalic{Swift} with \emphitalic{VIPER}, enabling a unified experience across GoTo apps
    \item Worked on the GoPay app in \emphitalic{Flutter}, supporting \italictext{130M daily users} with an enhanced user experience.
    \item Implemented a \emphitalic{Server Driven UI} for GoPay's homepage, enabling dynamic updates without app releases.
    \item Integrated in-house analytics framework utilising \emphitalic{ProtoBuffs}, reducing third-party dependencies and cutting costs by 30\%.
\end{tightemize}
\sectionsep

\textbf{\href{https://summerofcode.withgoogle.com/projects/6623823417311232}{\runsubsection{iOS Developer |}}} 
\descript{Google Summer of Code - VideoLAN \datetext{June '21 – Aug '21}}
\begin{tightemize}
    \item Worked on the "Continue Watching" feature in VLC media player for iOS, enhancing user retention and engagement.
    \item Worked with the \emphitalic{legacy codebase} and understanding \emphitalic{Objective-C} to fix bugs and implement features.
    \item Improved UI/UX using \emphitalic{UIKit}, aligning with Apple's design guidelines for a more intuitive user experience.
    % \item Participated in code reviews, ensuring adherence to best practices and maintaining code quality.
    % \item Contributed to documentation, improving onboarding for new developers in the VideoLAN community.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TECHNICAL CONTRIBUTIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Open Source}

\textbf{\runsubsection{\href{https://github.com/swiftlang}{SwiftLang |}}}
\descript{The Swift programming language - \linktext{https://github.com/swiftlang/swift-build/pulls?q=is:pr+author:swiftlysingh+}{GitHub} \datetext{Present}}
\begin{tightemize}
    \item Implemented new diagnostic flags within the Swift build system, improving error reporting and developer experience.
    \item Enhanced compiler compatibility by adding checks for Apple Clang and removing unsupported flags.
    % \item Contributed to Swift Information Architecture Project, unifying content and improving documentation accessibility.
    % \item Provided support and guidance to the Swift community on the forums, fostering collaboration and knowledge sharing.
\end{tightemize}
\sectionsep

%\textbf{\runsubsection{VideoLAN |}}
%\descript{The VLC media player - \linktext{https://code.videolan.org/videolan/vlc-ios/-/merge_requests?scope=all&state=merged&author_username=pushpinderpalsingh}{GitLab} \datetext{2021}}
%\begin{tightemize}
%     \item Developed UI/UX enhancements for VLC on iOS, including cast UI fixes and aspect ratio control feedback.
%     \item Improved compatibility of VLC on iOS by addressing issues related to home indicator behavior and emoji support.
%     \item Resolved key functional bugs in VLC for iOS, specifically related to play button behavior and video player alignment.
%\end{tightemize}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Technical Skills }
% \descript{Apple Platforms (Swift), Flutter, Open Source, DevOPs, Self-hosting, IoT, 3D Printing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\textbf{\href{[Link to project/repo]}{\runsubsection{ADHD Detection with Explainable AI |}}}
\descript{EEG Analysis}
\begin{tightemize}
    \item Developed a Transformer Encoder model in \emphitalic{TensorFlow} for enhanced ADHD detection from EEG data.
    \item Applied explainable AI techniques (e.g., \emphitalic{PathSHAP}) to interpret model decisions and improve clinical trust.
    \item Focused on improving both accuracy and interpretability, surpassing limitations of previous black-box models.
    \item Utilized publicly available EEG datasets (\emphitalic{ADHD Dataset, FOCUS Dataset, ADHD-200}) for rigorous evaluation.
    \item Preparing a research paper on the project findings for future publication.
\end{tightemize}
\sectionsep


\textbf{\href{https://apps.apple.com/app/artiweather/id6446815662}{\runsubsection{ArtiWeather |}}} 
\descript{An Art Weather App - \linktext{https://apps.apple.com/app/artiweather/id6446815662}{AppStore}}
\begin{tightemize}
    \item Developed ArtiWeather for iOS 18 using \emphitalic{SwiftUI}, achieving \italictext{1.2k downloads} and \italictext{5k organic impressions} on launch day.
    \item Integrated \emphitalic{on-device Stable Diffusion} using \emphitalic{CoreML} for weather-based image generation, with no server costs.
    \item Built beautiful widgets using \emphitalic{WidgetKit} for displaying weather and generated images on the home screen.
    \item Working on optimizing SD Model, enhancing download UX/UI, and adding support for additional cities.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\textbf{\runsubsection{Smart India Hackathon 2020 |}}
\descript{Winner \datetext{2021}}
\begin{tightemize}
    \item Built an AI IoT system to predict and adjust lighting and HVAC demand using sensors.
    \item SIH is a national hackathon by the Government of India, tackling real-world challenges.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Comment out original bibliography approach
\section{Publications}
\vspace{.5\baselineskip}
 \begin{tightemize} % <-- Using tightemize here
    \item A probabilistic routing-based secure approach for opportunistic iot network using blockchain. \\
    P. Rani, P. P. Singh, A. Balyan, V. Jain, D. Sangwan, and J. Shokeen. In \emphitalic{2020 IEEE 17th India Council International Conference (INDICON)}, pages 1--7, 2020. %\vspace{0.5em} % You might remove this if tightemize is enough

    \item A secure epidemic routing using blockchain in opportunistic internet of things. \\
    P. Rani, P. P. Singh, A. Balyan, J. Shokeen, V. Jain, and D. Sangwan. In A. Khanna, D. Gupta, Z. Pó\l{}kowski, S. Bhattacharyya, and O. Castillo, editors, \emphitalic{Data Analytics and Management}, pages 101--110, Singapore, 2021. Springer Singapore. %\vspace{0.5em} % You might remove this if tightemize is enough

 \end{tightemize}

 \sectionsep % Add space after publications






%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\runsubsection{MS in Computer Science |}
\descript{California State University, Sacramento \datetext{Aug '24 - May '26}}

\sectionsep
\runsubsection{BE in Computer Engineering |}
\descript{Netaji Subhas University of Technology \datetext{Aug '18 - May '22}}

\end{document}
